\huge Tor's Usability for Censorship Circumvention

### 2016-04-17 pets2017-paper/pets2017-paper.tex
edit comments.

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:05 \\
	E2-NEW & 18/19 & 95\% & 3:22 \\
	E2-OLD & 16/19 & 84\% & 5:07 \\
	E3-NEW & 13/20 & 65\% & 22:19 \\
	E3-OLD & 10/20 & 50\% & 40:08 \\
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned success time for 40 minutes.}
\label{table:participant-summary}
\end{table}

@@

% impacts of making bridge page collapsed 
This is unclear. And people didn't really see our advice that we put on the page.

>>>>

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\ % medians of only finished: 0:20 
	E1-OLD & 19/19 & 100\% & 1:05 \\ %medians of only finished: 1:01
	E2-NEW & 18/19 & 95\% & 3:22 \\ %medians of only finished: 3:22
	E2-OLD & 16/19 & 84\% & 5:07 \\ %medians of only finished: 3:13
	E3-NEW & 13/20 & 65\% & 22:19 \\ %medians of only finished: 12:38
	E3-OLD & 10/20 & 50\% & 40:08 \\ %medians of only finished: 18:16 
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned success time for 40 minutes.}
\label{table:participant-summary}
\end{table}

@@

% impacts of making bridge page collapsed 
This is unclear.
